On the Duality of Frequentist Point Estimates and Bayesian Shrinkage Priors: An Extension based on the Triple-Gamma-Prior

### 2024-06-12 01_latex/MScThesis_Econ.tex
Safety Commit

\clearpage
\thispagestyle{plain}
\tableofcontents
\pagebreak
\setcounter{savepage}{\arabic{page}}
\pagenumbering{arabic}

@@

%----- Literature Review -----
\section{Literature Review}

@@

The third and final hyper-parameter $\kappa_B$ enters the Triple-Gamma-Penalty $J_{TG}(\beta)$ as part of $\phi^\xi = \frac{2c^\xi}{\kappa_B^2 a^\xi}$ as can be seen from equation \ref{eq:tgr}. Notably, $\kappa_B$ is squared and thus only the absolute value of $\kappa_B$, $|\kappa_B|$, influences the structure of the penalty.

\begin{figure}[!h]
\centering
\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInKappa.png}
\caption{Triple-Gamma-Penalty using different values of $\kappa_B$}
\label{fig:basicTGPen}
\end{figure}

\newpage
%---- Table Summarizing the Effects of Changes in the Hyperparameters
\begin{landscape}
\begin{table}[!h]
\begin{center}
\begin{tabular}{lcccccc}\toprule
		& \multicolumn{2}{l}{Change} & \multicolumn{3}{c}{Mathematical Properties}\\
		\cmidrule(r{4pt}){2-3} \cmidrule(l){4-5}
Variable     	& \textbf{Positive} Change  & \textbf{Negative} Change & Defined Range & Misc.\\\midrule
$a^\xi$  	& \makecell{Shifting towards\\ \textit{Gaussian}-like behaviour\\ at $\beta = 0$} & \makecell{Shifting towards singularity\\ at $\beta = 0$; Higher\\ immediate penalty for coefficients\\ $\beta \neq 0$} & $(0.5, \infty)$ & Expl.\\
$c^\xi$ 		& \makecell{Generally, convergence towards \\ convexity and, given certain \\ settings for $a^\xi$ and\\ $\kappa_B$, LASSO. Higher values\\ increase the additional penalty\\ for higher absolute values of $\beta$.} &  \makecell{For values smaller \\ than $0.1$, similar effect\\ to increase in $a^\xi$} & $(0, \infty)$ & Expl. \\
$\kappa_B$ 	& 15883 & 5.2e-8 & $(-\infty, \infty)/{0}$ & Expl. \\\bottomrule
\end{tabular}
\caption{Summary of the effects of changes in the hyperparameters $a^\xi$, $c^\xi$ and $\kappa_B$ on the penalty structure}
\label{tab:VariationsInHyperparameters}
\end{table}
\end{center}
\end{landscape}
\newpage

@@

\begin{figure}[!h]
\centering
\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/ComparisonToOtherPenalties.png}
\caption{Basic Representation of the Triple-Gamma-Penalty using Hyperparameters $c^\xi = 0.1, \kappa_B = 2, a^\xi = 0.75$ compared to \textit{LASSO} and \textit{Ridge} Penalties}
\label{fig:basicTGPen}
\end{figure}

@@

%----- Small Applied Section
\section{Small Applied Section}
Here I am planning to apply the TGP using Peter's Bayesian Package and the self coded frequentist code on a small dataset.
\section{Conclusion}
\section{Possible Extensions and Criticism}
\section{References}

>>>>

\clearpage

\section*{Acknowledgements}
\thispagestyle{empty}

I like to acknowledge ...

\clearpage

\thispagestyle{plain}
\tableofcontents
\pagebreak
\setcounter{savepage}{\arabic{page}}
\pagenumbering{arabic}

@@

%----- Literature Review -----
\section{Literature Review}\label{sec:litreview}

@@

The third and final hyper-parameter $\kappa_B$ enters the Triple-Gamma-Penalty $J_{TG}(\beta)$ as part of $\phi^\xi = \frac{2c^\xi}{\kappa_B^2 a^\xi}$ as can be seen from equation \ref{eq:tgr}. Notably, $\kappa_B$ is squared and thus only the absolute value of $\kappa_B$, $|\kappa_B|$, influences the structure of the penalty. The overall third function value is defined as $\frac{\beta_j^2}{2\phi^\xi}$ and by plugging in $\phi^\xi$ we get $\frac{\beta_j^2\kappa_ B^2a^\xi}{4c^\xi}$, it can be seen that a value of $\kappa_B = 0$ leads to the entire parameter value being zero for all values of $\beta_j$. Hence, a change in $\beta_j$ won't influence the penalty and furthermore won't have an influence on the overall risk minimization problem, the result being that the optimal set of parameters will only depend on the chosen loss function.\\

For all values of $\kappa_B \neq 0$, the value of the hyper-parameter will influence the penalty structure. A plot with several different values for the absolute value of $\kappa_B$ can be found in figure \ref{fig:TGPenalty_ChangeInKappa}.

\begin{figure}[t]
\centering
\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_ChangeInKappa.png}
\caption{Triple-Gamma-Penalty using different values of $\kappa_B$}
\label{fig:TGPenalty_ChangeInKappa}
\end{figure}

\newpage
%---- Table Summarizing the Effects of Changes in the Hyperparameters
\begin{landscape}
\begin{table}[!h]
\begin{center}
\begin{tabular}{lcccccc}\toprule
		& \multicolumn{2}{l}{Change} & \multicolumn{3}{c}{Mathematical Properties}\\
		\cmidrule(r{4pt}){2-3} \cmidrule(l){4-5}
Variable     	& \textbf{Positive} Change  & \textbf{Negative} Change & Defined Range & Misc.\\\midrule
$a^\xi$  	& \makecell{Shifting towards\\ \textit{Gaussian}-like behaviour\\ at $\beta = 0$} & \makecell{Shifting towards singularity\\ at $\beta = 0$; Higher\\ immediate penalty for coefficients\\ $\beta \neq 0$} & $(0.5, \infty)$ & Expl.\\
$c^\xi$ 		& \makecell{Generally, convergence towards \\ convexity and, given certain \\ settings for $a^\xi$ and\\ $\kappa_B$, LASSO. Higher values\\ increase the additional penalty\\ for higher absolute values of $\beta$.} &  \makecell{For values smaller \\ than $0.1$, similar effect\\ to increase in $a^\xi$} & $(0, \infty)$ & Expl. \\
$\kappa_B$ 	& 15883 & 5.2e-8 & $(-\infty, \infty)/\{0\}$ & Expl. \\\bottomrule
\end{tabular}
\caption{Summary of the effects of changes in the hyperparameters $a^\xi$, $c^\xi$ and $\kappa_B$ on the penalty structure}
\label{tab:VariationsInHyperparameters}
\end{center}
\end{table}
\end{landscape}
\newpage

@@

As already mentioned in section \ref{sec:litreview}, several other penalty terms have already been widely studied in the literature. Convex penalties like \textit{Ridge} \parencite{HoerlKennard1970a} or non-convex penalties like the \textit{Ar(c)tan} \parencite{WangZhu2016} and Gaussian \parencite{JohnVettamWu2022} have managed to establish itself as prominent approaches to regularization. It is now certainly of interest to see how the \textit{Triple-Gamma} penalty compares to the established methods. Seeing that, due to its flexibility, there is not \textit{one} \textit{Triple-Gamma} penalty, three distinct hyper-parameter setting have been chosen to represent the proposed penalty term.

\begin{figure}[!h]
\centering
\includegraphics[scale=0.75]{../02_simulation/021_simulation_figures/TGPenalty_Comparison.png}
\caption{Basic Representation of the Triple-Gamma-Penalty using Hyperparameters $c^\xi = 0.1, \kappa_B = 2, a^\xi = 0.75$ compared to \textit{LASSO} and \textit{Ridge} Penalties}
\label{fig:basicTGPen}
\end{figure}

@@

%----- Small Applied Section
%\section{Small Applied Section}
%Here I am planning to apply the TGP using Peter's Bayesian Package and the self coded frequentist code on a small dataset.
\section{Possible Extensions and Criticism}
\section{Conclusion}

\newpage
\section{List of Figures}
\listoffigures

\newpage
\section{List of Tables}
\listoftables

\newpage
\section{References}
